---
title: "Medical Accessibility with amapGeocode"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Medical Accessibility with amapGeocode}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette demonstrates a reproducible workflow for medical accessibility
analysis in China using `amapGeocode`, centred on:

1. Request caching + audit logging
2. OD matrix construction via the AutoNavi distance API
3. Preparing outputs for downstream accessibility metrics (e.g., the
   `{accessibility}` package)
4. Explainable geocode resolution and uncertainty sensitivity

## Setup

```{r, eval = FALSE}
library(amapGeocode)

# Set your AutoNavi API key
options(amap_key = "YOUR_KEY")

# Reproducible infrastructure
amap_cache_enable(path = tempdir(), ttl_days = 30)
amap_audit_enable(path = tempdir())

# Respect AutoNavi QPS limits (defaults are safe)
amap_config(throttle = TRUE, max_active = 3)
```

## Sample data

The package ships small example datasets:

```{r, eval = FALSE}
origins <- read.csv(system.file("extdata", "origins_sample.csv", package = "amapGeocode"))
destinations <- read.csv(system.file("extdata", "hospitals_sample.csv", package = "amapGeocode"))
```

## Explainable geocode resolution (optional)

When geocoding ambiguous Chinese queries, use `mode = "all"` to obtain
candidates and then resolve them with an explainable strategy.

```{r, eval = FALSE}
candidates <- getCoord("朝阳区", mode = "all")
resolved <- resolveGeocode(
  candidates,
  admin = list(province = "北京市", city = "北京市")
)
resolved$best
resolved$diagnostics
```

## Build OD matrix

```{r, eval = FALSE}
od <- getOdMatrix(
  origins = origins,
  destinations = destinations,
  mode = "driving"
)
od
```

## Prepare for {accessibility}

```{r, eval = FALSE}
od_acc <- asAccessibilityInput(od, origins = origins, destinations = destinations)
head(od_acc)
```

## Uncertainty sensitivity (top-2)

If upstream geocoding is ambiguous, you can propagate top-2 candidate
uncertainty to OD outputs.

```{r, eval = FALSE}
pu <- propagateUncertainty(
  best = resolved$best,
  candidates = resolved$candidates,
  destinations = destinations,
  mode = "driving"
)
head(pu$od_scenarios)
head(pu$od_summary)
```

## Audit report

```{r, eval = FALSE}
amap_audit_report(file.path(tempdir(), "amap_audit_report.csv"), format = "csv")
```
